Map/Reduce for the common man

### 2010-02-18 doc/slides.tex
a new figure and intro to cores/network slide added [KK]

@@

\begin{frame}\frametitle{}
  TODO: introduce cores/network idea
\end{frame}

>>>>

\begin{frame}\frametitle{}
  \begin{center}
    \includegraphics[width=\textwidth]{mr-new}
  \end{center}
\end{frame}

@@

\begin{frame}\frametitle{Cores \& Networks}
  Our map/reduce library works seemlessly across

  \bigskip
  \begin{itemize}
  \item multiple processor cores on the same (module \texttt{Cores})
    machine
    \begin{itemize}
    \item user just needs to specify the number of cores to be used
    \item uses Ocaml's \texttt{Unix} module
    \end{itemize}

    \bigskip
  \item networked cluster of machines (module \texttt{Network})
    \begin{itemize}
    \item user specifies the machine name(s) to be used
    \item relies on OCaml's \texttt{Unix} and \texttt{Marshal} modules
    \end{itemize}
  \end{itemize}
\end{frame}
